### 2021-12-01 plos_latex_template.tex
RJ: Minor edits until rule 10

%Rocío: Main idea: Use inclusive language
Inclusive language--language free from words, phrases or tones that reflect prejudiced or discriminatory views of particular people or groups--should be used in all communications \cite{hallDesigningDiversityInclusion2019}. 
Become familiar with the terminology used for disabilities, racialized groups, and gender and sexual orientations, and with the terms that should be avoided. %
Do not expect minoritized people to teach you--it's not their role--, and accept feedback without being offended.
Inclusive language also encompasses avoidance of excessive and too specific technical jargon and acronyms. 
%
% links, examples, this changes with the context
%practice: create a standards in inclusive language for your community, to build collective knowledge than can be passed to

@@

% Rocío: main idea: Budgets are limited and need to choose priorities.
Allocation of resources to support the goals of inclusion of the conference has to be intentional. 
Estimate the costs for these practices and define your priorities in advance (e.g. paying the organizing team, Code of Conduct training, captioning).
Additional support for attendees could also be considered in the budget: child care support, transportation fees, visa-related support (if in-person), internet connection services (for the virtual component). 
Consider that an online conference might reduce organization costs (e.g. no rental costs for a physical venue), allowing to redirect the money towards other inclusive priorities. 
When asking for sponsorship, it might be easier to justify supporting concrete actions towards inclusion than making generic demands for funding.

% Conference budgets are limited and rely mostly on sponsorship and attendance fees.

% Rocío: main idea: help take the burden out of participants for more inclusive participation
When determining the registration rates, the socioeconomic context of participants, their country of origin, and their career status should be taken into account  \cite{sarabipourChangingScientificMeetings2021, andalibPostdocQueueLabour2018, kaplanPostdocNot2012}
(see \cite{canelon2021cost} for an example of conversion rates based on country of origin and career status).

Resources permitting, allow the possibility of a `pay what you can' option. You could also aim to have a conference with no registration costs; this is especially true for online events, but bear in mind that free events have a lower attendance rate than non-free events \cite{eventbrite_ultimate_2017}. 
%Other costs can be prohibitive-> scholarships
Scholarships to attend the in-person component of the conference are an additional way to boost participation of people from marginalized groups, by offering support for travel and lodging expenses.
Design the diversity-related scholarship to be explicit about the groups you want to support, and be transparent about the criteria for evaluation to avoid self-selection (the fact that some people refrain from applying because they think they don't stand a chance). 
Conferences usually ask for cover letters or applications to assign these scholarships, and this can be a time-consuming, emotionally-demanding task. 
Simplify as much as you can the process of asking for financial support; 
people who do not have the time (e.g., because they have family responsibilities) might decide not to apply if the process is overtly complicated. 
Bear in mind that transferring money internationally is a cumbersome administrative process that can significantly augment the burden of already marginalized groups. Whenever possible, facilitate ways around money transfer (e.g., book flights, hotel reservations, waive conference fees).

@@

A conference can make a difference in the path towards inclusion/Conferences are powerful community-building spaces, that can foster change in future events and the community itself. The organizers of a conference edition and selection committees should do their best to pass their knowledge on best practices and problems encountered to future organizers.

@@

% Rocío: main idea: no first attempt is guaranteed to succeed
Assess whether equity and inclusion goals were met during the conference. 
Part of it can be done internally by evaluating the diversity indicators you defined at the beginning of the planning process. % examples

% Ask for feedback to know the extent of your success
Ask for feedback about the conference experience of the participants by posting a survey during and after the conference. 
Make open answer options to let people self-identify and express their opinions freely. Let all responses be optional and anonymous and commit to confidentiality and data privacy. 
The survey results will allow you to identify the aspects that worked towards your inclusion goals, and understand what went wrong and how people were excluded.
Do not expect everything to be perfectly inclusive, or to encompass all the dimensions of diversity at once. %You're part of a process and contributing to structural change.

% Pass the information
Document your processes, lessons, and guides in blog posts, reports, and presentations. 
Facilitate contacts with the people you worked with along the process. 
Make sure to share this information with future organizers,
they will have a starting point and their work to improve inclusion in the following editions of the conference will be easier.
If you are part of a stable meetings committee, encourage organizers to follow these rules and advocate for setting up new standards for inclusion. 
%hablar del pasado - shoulder of people before, federico
%sale? Most importantly, there are systemic discrimination issues at higher levels (e.g. society, academia) that one conference cannot change. 
%\la{Due to these systemic problems, even the minimum changes to how conferences have been historically organized will find resistance}, but your courage to make changes will be a step towards a more diverse and inclusive community, and can have a huge impact in the lives and careers of often excluded and minoritized people.

>>>>

%Rocío: Main idea: Use inclusive language
Inclusive language--language free from words, phrases or tones that reflect prejudiced or discriminatory views of particular people or groups--should be used in all communications \cite{hallDesigningDiversityInclusion2019}. 
Become familiar with the terminology used for disabilities, racialized groups, and gender and sexual orientations, and with the terms that should be avoided. %
Do not expect minoritized people to teach you--it's not their role--, and accept feedback without being offended.
Inclusive language also encompasses avoidance of excessive and too specific technical jargon and acronyms. 
% links, examples, this changes with the context
%practice: create a standards in inclusive language for your community, to build collective knowledge than can be passed to

@@

% Rocío: main idea: Need to budget for inclusive practices.
Allocation of resources to support the goals of inclusion of the conference has to be intentional. 
Estimate the costs for these practices and define your priorities in advance (e.g. paying the organizing team, Code of Conduct training, captioning).
Additional support for attendees could also be considered in the budget: child care support, transportation fees, visa-related support (if in-person), internet connection services (for the virtual component). 
Consider that an online conference might reduce organization costs (e.g. no rental costs for a physical venue), allowing to redirect the money towards other inclusive priorities. 
When asking for sponsorship, it might be easier to justify supporting concrete actions towards inclusion than making generic demands for funding.

% Rocío: main idea: help take the burden out of participants for more inclusive participation
When determining the registration rates, the socioeconomic context of participants, their country of origin, and their career status should be taken into account  \cite{sarabipourChangingScientificMeetings2021, andalibPostdocQueueLabour2018, kaplanPostdocNot2012}
(see \cite{canelon2021cost} for an example of conversion rates based on country of origin and career status). 
Resources permitting, allow the possibility of a `pay what you can' option. You could also aim to have a conference with no registration costs; this is especially true for online events, but bear in mind that free events have a lower attendance rate than non-free events \cite{eventbrite_ultimate_2017}. 
%Other costs can be prohibitive-> scholarships
Scholarships to attend the in-person component of the conference are an additional way to boost participation of people from marginalized groups, by offering support for travel and lodging expenses.
Design the diversity-related scholarship to be explicit about the groups you want to support, and be transparent about the criteria for evaluation to avoid self-selection (the fact that some people refrain from applying because they think they don't stand a chance). 
Conferences usually ask for cover letters or applications to assign these scholarships, and this can be a time-consuming, emotionally-demanding task. 
Simplify as much as you can the process of asking for financial support; 
people who do not have the time (e.g., because they have family responsibilities) might decide not to apply if the process is overtly complicated. 
Bear in mind that transferring money internationally is a cumbersome administrative process that can significantly augment the burden of already marginalized groups. Whenever possible, facilitate ways around money transfer (e.g., book flights, hotel reservations, waive conference fees).

@@

A conference is a critical community-building space, and can foster change in future events and the community itself. The organizers of a conference edition and selection committees should do their best to pass their knowledge on best practices and problems encountered to future organizers.

@@

% Rocío: main idea: assess how inclusive was the conference
Assess whether equity and inclusion goals were met during the conference. 
You can rely on the diversity indicators defined at the beginning of the planning process (rule 1). 
It is likely that you will be able to calculate some of your indicators directly from information that you have already collected from your organizing team, speakers, and others (e.g. countries of origin, or preferred language).
Other indicators may need a special survey asking for additional information and feedback about the conference. 
In the survey, providing options for open answers will allow people to express their opinions freely, and may give you more insights into how/why your inclusion practices worked or did not work. 
% Do not expect everything to be perfectly inclusive, or to encompass all the dimensions of diversity at once. %You're part of a process and contributing to structural change.

% Pass the information
Document your processes, outcomes, and lessons learned in blog posts, reports, and presentations. 
Make sure to share this information with future organizers, as well as the contact information of the people you worked with--if they agree to it, to give them a starting point to improve inclusion in the following editions of the conference.
If you are part of a stable meetings committee, encourage organizers to follow these rules and set up new standards for inclusion: be explicit on the inclusive spirit of the conference and the practices that future organizers should commit to when publishing the call for conference organization and the selection criteria. 
%something about the past - shoulder of people before, federico
